MLH1 Data Report

### 2018-05-30 Main_Report.rmd
passed mice are colored light red

@@

@@

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") 
  #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
  plot_list[[h]] =   pf
}

>>>>

#quant_status (this isn't saving)
#for(i in 1:length(MLH1_data$mouse)){
#  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
#}

@@

MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

@@

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], y= adj_nMLH1.foci, x= quality, aes(colour = factor(Batch)), width = 0.25)
  # +   geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5)

  + geom_jitter()
  + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") + scale_fill_manual(values=c(NA, "red"), breaks=NULL)

# +    geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))

  plot_list[[h]] =   pf
}

#orig
plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf +geom_rect(data = df_list[[h]], aes(fill=quant_status), xmin=-100, xmax=100, ymin=-100, ymax=100, alpha=0.005)

    pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +

    scale_fill_manual(values=alpha(c("red"), .005), breaks=NULL)

    #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
  plot_list[[h]] =   pf
}
#can't change the alpha/transparency of the red rec
